A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-13 docs/icccn2009/paper.tex
Added ding-symbols
git-svn-id: svn://localhost/netbeams/trunk@382 559edde2-a4d4-44e0-96fc-4035e40d7396

\usepackage{epsfig}
\usepackage{fancyvrb}
\usepackage{url}

@@

Our implementation of the DSP is based on the Open Source
implementation of OSGi called Knopflerfish \cite{knopflerfish01}.
Since Sun Microsystems does not support its JDK for the Gumstix, we
use JamVM \cite{jamvm01} as the Java virtual machine implementation
and GNU Classpath \cite{classpath01} for the runtime libraries. We
have implemented various DSP Components that implement the
functionality needed for NetBEAMS. On the far left of Figure
\ref{FIG_NETBEAMS} is the actual sensor; in our case the
aforementioned YSI Sonde. The YSI Sonde DP (1) uses the RS232 standard
to read the physical measurements from the device over a serial port.
This component converts the physical measurements into a DSP-specific
message. Figure \ref{FIG_DSP_YSI_DATA} depicts the YSI Sonde's
specific message format which includes each measurement data point,
described in Table \ref{TAB_SONDE_MEASUREMENTS}.

@@

The SondeDataContainerType defines the payload of messages generated
by the YSI Sonde DP. As all DSP messages, it is derived from the
AbstractMessageContent. The payload mainly consists of the
SondeDataType that defines all the sensor data that the YSI Sonde is
capable of producing. The YSI Sonde DP uses the RS232 to query the
physical device for its data in regular intervals. The measurements
are then converted into a DSP message and forwarded to the DSP Broker
from there they are forwarded to the remote communication component
described in the next section.  The YSI Sonde DP can also be
configured via special DSP messages, to direct the Sonde to change its
sampling frequency.  These property messages originate from a web
management interface (component (6) in Figure \ref{FIG_NETBEAMS}).

@@

All messages sent by the YSI Sonde DP need to be uploaded to a remote
database. Since the DSP itself can only handle communication within
its local DPs and DCs, we have created a matching pair of DC and DP
that can handle remote communication (components (2) and (3) in Figure
\ref{FIG_NETBEAMS}). As explained earlier, we make use of the cellular
phone network to upload sensor data to a remote backend server. While
the cellular phone network has sufficient coverage for more
environmental sensor networks, it is not cost effective to keep a data
link permanently open. The remote communiction components can be
configured to upload buffered sensor data only in certain time
intervals. Messages are transported via HTTP \cite{RFC2068}. The
matching DP/DC pair for remote communication has the following
properties:

>>>>

\usepackage{epsfig}
\usepackage{fancyvrb}
\usepackage{url}
\usepackage{pifont}

@@

Our implementation of the DSP is based on the Open Source
implementation of OSGi called Knopflerfish \cite{knopflerfish01}.
Since Sun Microsystems does not support its JDK for the Gumstix, we
use JamVM \cite{jamvm01} as the Java virtual machine implementation
and GNU Classpath \cite{classpath01} for the runtime libraries. We
have implemented various DSP Components that implement the
functionality needed for NetBEAMS. On the far left of Figure
\ref{FIG_NETBEAMS} is the actual sensor; in our case the
aforementioned YSI Sonde. The YSI Sonde DP \ding{192} uses the RS232 standard
to read the physical measurements from the device over a serial port.
This component converts the physical measurements into a DSP-specific
message. Figure \ref{FIG_DSP_YSI_DATA} depicts the YSI Sonde's
specific message format which includes each measurement data point,
described in Table \ref{TAB_SONDE_MEASUREMENTS}.

@@

The SondeDataContainerType defines the payload of messages generated
by the YSI Sonde DP. As all DSP messages, it is derived from the
AbstractMessageContent. The payload mainly consists of the
SondeDataType that defines all the sensor data that the YSI Sonde is
capable of producing. The YSI Sonde DP uses the RS232 to query the
physical device for its data in regular intervals. The measurements
are then converted into a DSP message and forwarded to the DSP Broker
from there they are forwarded to the remote communication component
described in the next section.  The YSI Sonde DP can also be
configured via special DSP messages, to direct the Sonde to change its
sampling frequency.  These property messages originate from a web
management interface (component \ding{197} in Figure \ref{FIG_NETBEAMS}).

@@

All messages sent by the YSI Sonde DP need to be uploaded to a remote
database. Since the DSP itself can only handle communication within
its local DPs and DCs, we have created a matching pair of DC and DP
that can handle remote communication (components \ding{193} and \ding{194} in Figure
\ref{FIG_NETBEAMS}). As explained earlier, we make use of the cellular
phone network to upload sensor data to a remote backend server. While
the cellular phone network has sufficient coverage for more
environmental sensor networks, it is not cost effective to keep a data
link permanently open. The remote communiction components can be
configured to upload buffered sensor data only in certain time
intervals. Messages are transported via HTTP \cite{RFC2068}. The
matching DP/DC pair for remote communication has the following
properties:
